---
title: "Lab 6"
author: "Cristina Robinson"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator. 

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```
Try a t-test:
```{r}
t.test(gp_1, gp_2)
```
What is the meaning of the p-value?

This p-value of 0.1982 means: If these samples were drawn from populations with the same mean, the probability of taking 2 random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%. 

Retain (fail to reject) the null hypothesis. >> There is no significant difference in means between group 1 and group 2. 

Warning: people get weirdly upset if you say "accept" the null. 

Now let's compare this outcome to a rank-based test. 

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

If these samples were drawn from populations with the same ranks (medians), the probability of finding 2 samples with the same ranks *at least as different* as those in our samples is 0.28.

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2 (statistical summary). 

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: (U(df) = 86, p = 0.28)).


## Linear Regression 

Simple linear regression (single dependent variable, a single independent variable)

```{r}
# make an exploratory plot of penguin body mass (y-axis) versus flipper length (x-axis)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Find a linear regression model using ordinary least squares desribing the relationship between flipper length and body mass for these penguins. 

3 pieces: 

- What type of model? 
- What is the relationship to model (DV ~ IV(s))
- Where is the data that's used to create this model? 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
```


### Broom package returns model outputs as tidy data frames
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

broom::glance(penguin_lm) # talk about these next week in lecture
```
How can I actually include my model equation in a report?

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```



